Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Update XFOIL repo information

\bibitem[Bachant and Wosnik(2015)]{Bachant2015-NACAXX20-XFOIL} Bachant, P.;
Wosnik, M. \newblock NACA XX20 XFOIL Coefficients. \newblock Zenodo. Available
online: \url{http://dx.doi.org/10.5281/zenodo.32054} (accessed on 1 November
2015).

>>>>

\bibitem[Bachant and Wosnik(2016)]{Bachant2015-NACAXX20-XFOIL} Bachant, P.;
Wosnik, M. \newblock NACA XX20 XFOIL Coefficients. \newblock Zenodo. Available
online: \url{http://dx.doi.org/10.5281/zenodo.45099} (accessed on 22 January
2016).
